Tidy data structure to support exploration and modeling of temporal-context data

### 2018-10-08 main.Rmd
minor tweak on code reasoning
added more plots to flights data

```{r map-airlines, fig.cap = "(ref:map-airlines-cap)"}
```

(ref:map-airlines-cap) An overview of US airline traffic in 2017. Points indicate locations of airports, and lines the connecting routes across the country. There are a few hubs connecting most airlines and sporadic airports.

@@

```{r glimpse}
```

@@

```{r tsibble, echo = TRUE}
```

@@

```{r quantile, echo = TRUE}
```

@@

This pipeline chains four verbs. A set of succinct verbs makes the composition self-explanatory: (1) `index_by()` + `summarise()`: compute 50%, 80% and 95% quantiles for every hour; (2) `mutate()`: add time components that are extracted from the index; (3) `gather()`: melt different quantiles into a long form. Step (2) and (3) prepare the data for visualisation later. Every verb generates the output of the same type of the input, making chaining possible. Once the initial setup is done, the program takes care of updating the index and key, and empowers users concentrate on the substance of data analysis. Every one else who do not write the code would find the code fairly easy to comprehend.

@@

>>>>

<!-- 
```{r map-airlines, fig.cap = "(ref:map-airlines-cap)"}
```

(ref:map-airlines-cap) An overview of US airline traffic in 2017. Points indicate locations of airports, and lines the connecting routes across the country. There are a few hubs connecting most airlines and sporadic airports.
-->

@@

@@

```{r tsibble}
```

```{r carrier-delayed}
```

```{r carrier-mosaic}
```

```{r nyc-flights}
```

```{r nyc-delay}
```

```{r nyc-monthly-1}
```

```{r nyc-monthly-2}
```

```{r nyc-monthly-plot}
```

@@

```{r quantile}
```

@@

This pipeline chains four verbs. A set of succinct verbs makes the composition self-explanatory: (1) `index_by()` + `summarise()`: compute 50%, 80% and 95% quantiles for every hour; (2) `mutate()`: add time components that are extracted from the index; (3) `gather()`: melt different quantiles into a long form. Step (2) and (3) prepare the data for visualisation later. Every verb generates the output of the same type of the input, making chaining possible. Once the initial setup is done, the program takes care of updating the index and key, and empowers users concentrate on the substance of data analysis. The one who write the code would easily reason about the code and every one else would find the code fairly easy to comprehend.

@@

```{r draw-qtl-prep}
```
